Flexibility of interactions depends on habitat suitability

### 2019-08-30 paper/manuscript.Rmd
Nicer first paragraph

From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
On one end of the spectrum, generalist are have traits that allow them to intract a large number of species.
In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
This is so because, on the other end of the spectrum, specialist species tend to have a have deeper co-evolutionary history with their partner species. 
This in turn is reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.

>>>>

From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
On one end of the spectrum, generalist species have traits that allow them to interact with a large number of species.
In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
On the other end of the spectrum, specialist species are thought to have a more deep-rooted co-evolutionary history with their partner species. 
This tighter co-evolution, in turn, can be reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.
This niche-based rationale can also operate within a species. 
We can expect that a species can obtain a higher benefit from interactions with species with traits that better match their requirements.
